Paper Report

### 2017-11-10 Paper_report.tex
Papers

%----------------------------------------------------------------------------------------
%	IBM models
%----------------------------------------------------------------------------------------
IBM models

@@

>>>>

%----------------------------------------------------------------------------------------
%	IBM models
%----------------------------------------------------------------------------------------

@@

\section{Overview about statistical alignment}
\subsection{General problem}
Input:
\begin{itemize}
\item A source sentence: $f_1^J = f_1,...,f_j,...f_J$
\item A target sentence: $e_1^I = f_1,...,f_i,...f_I$
\end{itemize}
Output: Alignment map $j \rightarrow i = a_j$
\begin{itemize}
\item An alignment: $a_1^J = a_1,...,a_j,...a_J$
\end{itemize}

\subsubsection{}
Our work is modelling the relationship between a source sentence and a target sentence. \\
We start from the view of translation model, which is finding this best translation $e_1^I$ for a source sentence $f_1^J$.
\begin{equation}
e_1^I = argmax_{e_1^I} p(e_1^I|f_1^J) = argmax_{e_1^I} \frac{p(f_1^J|e_1^I)p(e_1^I)}{p(f_1^J)}
\end{equation}

In this case, the translation direction is changed from $p(e_1^I|f_1^J)$ to $p(f_1^J|e_1^I)$. This should be noted while reading alignment papers. \\

From now, the work of translation is modelling $p(f_1^J|e_1^I)$. Our work is more complicated by adding an alignment component $a_1^J$ which maps from a source position j to a target position $a_j$ (It could be i, but there is also empty words).

\begin{equation}
p(f_1^J|e_1^I) = \sum_{a_1^J} p(f_1^J, a_1^J|e_1^I)
\end{equation}

With the model parameters $\theta$, our main problem becomes $p_{\theta}(f_1^J, a_1^J|e_1^I)$

\subsubsection{Problem of empty word}

\subsection{Hidden Markov Alignment Model}
The alignment model is re-structured:
\begin{equation}
p(f_1^J, a_1^J|e_1^I) = p(J|e_1^I) \prod_{j=1}^J p(f_j, a_j | f_1^{j-1}, a_1^{j-1}, e_1^I)
\end{equation}
\begin{equation}
= p(J|e_1^I) \prod_{j=1}^J p( f_j | f_1^{j-1}, a_j, e_1^I) * p( a_j | f_1^{j-1}, a_1^{j-1}, e_1^I)
\end{equation}

For this new structure, there are three different probabilities:
\begin{itemize}
\item $p(J|e_1^I)$ : Length probability
\item $p( f_j | f_1^{j-1}, a_j, e_1^I)$ : Lexicon  probability
\item $p( a_j | f_1^{j-1}, a_1^{j-1}, e_1^I)$ : Alignment probability
\end{itemize}

We need some assumptions to put this model into HMM:
\begin{itemize}
\item $p( f_j | f_1^{j-1}, a_j, e_1^I) \rightarrow p(f_j | e_{a_j}) $ : The lexicon probability depends only on the word at position $a_j$
\item $p( a_j | f_1^{j-1}, a_1^{j-1}, e_1^I) \rightarrow p(a_j | a_{j-1}, I) $ : The alignment $a_j$ depends on $a_{j - 1}$  (First-order dependence)
\item $p(J|e_1^I) \rightarrow p(J|I)$ : Simplify this probability (Not because of HMM, it's just simplification)
\end{itemize}

Therefore, $p(f_1^J, a_1^J|e_1^I)$ is decomposed under these assumptions as follows:

\begin{equation}
p(f_1^J, a_1^J|e_1^I) = p(J|I) \prod_{j=1}^J p(f_j | e_{a_j}) * p(a_j | a_{j-1}, I)
\end{equation}
